---
title: "Prediction Assignment"
author: "Gehad Mohsen"
date: "11/30/2019"
output: html_document
---

# Loading data

```{r}
data_train <- read.csv("pml-training.csv")
data_test  <- read.csv("pml-testing.csv")

```

# Loading required packages 

```{r}
library(dplyr)
library(caret)
library(randomForest)
library(e1071)

```


# Data Preprocessing

Cleaning all the variables with missing values and irrevelant variables

```{r}
gooddata<-names(data_test[,colMeans(is.na(data_test))==0])[8:59]

training_data <- data_train[,c(gooddata,"classe")]
testing_data <-data_test[,c(gooddata,"problem_id")]

```

# Cross validation

Use 70% of training set data to built a model, and use the rest to test the model

```{r}
set.seed(100)
inTrain <- createDataPartition(y=training_data$classe,p=.70,list=F)
TrainingSet <- training_data[inTrain,]
TestingSet <- training_data[-inTrain,]

```

# Building the Model 

Use Random Forest method (RF)

```{r}

# Fitting model
model1 <- randomForest(classe ~., data=TrainingSet, method="class")

# Predicting
prediction1 <- predict(model1, TestingSet, Type="class")

# Testing
confusionMatrix(prediction1, TestingSet$classe)

```

The accuracy of the model is 99.58 % which is a high accuracy , so I will use this model in prediction for the quiz.
